---
title: "fiona_help"
author: "Francesca Tinsdeall"
date: "`r Sys.Date()`"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(tidyverse, 
               knitr,
               here,
               DT,
               readxl, 
               metafor,
               clubSandwich,
               orchaRd, 
               MuMIn,
               patchwork,
               GoodmanKruskal,
               networkD3,
               ggplot2,
               plotly,
               ggsignif,
               visdat,
               ggalluvial,
               ggthemr, 
               cowplot,
               grDevices,
               png,
               grid,
               gridGraphics,
               pander,
               formatR,
               rmdformats
               )

install.packages("pacman")
pacman::p_load(devtools, tidyverse, metafor, patchwork, R.rsp, emmeans)

devtools::install_github("daniel1noble/orchaRd", force = TRUE)
devtools::install_github('cttobin/ggthemr')

dat <- read.csv('meta_data.csv')
```


# Make variable to group effect sizes that come from same cohorts and same outcome measurements (but at different time points)

```{r}
SMD_new <- SMD %>% group_by(study_id_str, disease_cohort_str, control_cohort_str, outcome_id_str) %>% 
  mutate(different_times = n())
```

# Make variable to group effect sizes that come from same cohorts at same time point but from different outcome measures 

```{r}
SMD_new <- SMD_new %>% 
  ungroup() %>% 
  group_by(study_id_str, disease_cohort_str, control_cohort_str, time) %>% 
  mutate(different_outcome = n())

write.csv(SMD_new, 'meta.csv')
```

manipulation in excel to match up cohorts 

# Read in excel file

```{r}
SMD.g <- read.csv('meta.csv')
```

# Make variable that groups effect sizes that come from same outcome measurement protocol at the same time (but different cohorts)

```{r}
SMD_new <- SMD.g %>% 
  group_by(study_id_str, outcome_id_str, time) %>% 
  distinct()
  mutate(same_PPI_param_same_time_diff_coh = n())

write.csv(SMD_new, 'meta.csv')

SMD.g <- read.csv('meta.csv')

```

# Make variable that groups effect sizes that come from the same cohorts 

```{r}
SMD_new <- SMD.g %>% 
  group_by(study_id_str, disease_cohort_str, control_cohort_str) %>% 
  mutate(cohort = n())

write.csv(SMD_new, 'meta.csv')
SMD.g <- read.csv('meta.csv')
```






#not done below in most current meta dataset






```




